Incentivizing Exploration with Unbiased History

### 2018-11-01 3levelproofs.tex
q_a -> \fdpN
fun fact: we now have at most 30 q's in the paper

\begin{proof}[Proof of Lemma~\ref{3levelw1}]
  For the $s$-th first-level group, define $W_1^{a,s}$ to be the event
  that the number of arm $a$ pulls in the $s$-th first-level group is
  between $q_a T_1- \GdT \sqrt{T_1\log(T)}$ and
  $q_a T_1 + \GdT \sqrt{T_1\log(T)}$. By Lemma~\ref{lem:t1runs}
\[
\Pr[W_1^{a,s}] \geq 1-2\exp(-2\log(T)) \geq 1-2/T^2.
\]
Let $W_1$  be the intersection of all these events (i.e.
$W_1 = \bigcap_{a,s}W_1^{a,s}$). By union bound, we have
\[
\Pr[W_1] \geq 1- \frac{4S}{T^2}.
\]
\end{proof}

@@

\begin{proof}[Proof of Lemma~\ref{3levelw4}]
By Berry-Esseen Theorem and
  $\mu_a \in [1/3,2/3]$, we have for any $a$,
\[
\Pr[W_4^{s,a,high}] \geq (1-\Phi(1/2)) - \frac{5}{\sqrt{q_aT_1}} > 1/4.
\]
The last inequality follows when $T$ is larger than some constant.
Similarly we also have 
\[
\Pr[W_4^{s,a,low}] > 1/4.
\]
Since $W_4^{s,a,high}$ is independent with $W_4^{s,3-a,low}$, we have
\[
\Pr[W_4^{s,a,high} \cap W_4^{s,3-a,low}] =\Pr[W_4^{s,a,high}] \cdot  \Pr[W_4^{s,3-a,low}]>(1/4)^2 = 1/16.
\]
Notice that $(W_4^{s,a,high} \cap W_4^{s,3-a,low})$ are independent
across different $s$'s. By union bound, we have
\[
\Pr[W_4] \geq 1- 2(1-1/16)^S \geq 1 -2 /T.
\]
\end{proof}

@@

\begin{lemma}
  For the $s$-th first-level group and arm $a$, define
  $\bar{\mu}_a^{1,s}$ to be the empirical mean of arm $a$ pulls in
  this group. If $W$ holds, then
  \[
    |\bar{\mu}_a^{1,s} - \mu_a| \leq \sqrt{\frac{4\log(T)}{q_a T_1}}.
  \]
\end{lemma}

\begin{proof}
  The events $W_1$ and $W_2^{a,s,1,t}$ for
  $t = q_a T_1- \GdT \sqrt{T_1\log(T)},...,q_a T_1 + \GdT
  \sqrt{T_1\log(T)}$ together imply that
\[
|\bar{\mu}_a^{1,s} - \mu_a| \leq \sqrt{\frac{2\log(T)}{q_a T_1- \GdT \sqrt{T_1\log(T)}}} \leq \sqrt{\frac{4\log(T)}{q_a T_1}}.
\]
The last inequality holds when $T$ is larger than some constant.
\end{proof}

\begin{lemma}
  For each arm $a$, define $\bar{\mu}_a$ to be the empirical mean of
  arm $a$ pulls in the first two levels. If $W$ holds, then
  \[
    |\bar{\mu}_a - \mu_a| \leq \sqrt{\frac{4\log(T)}{S q_a T_1}} .
  \]
Furthermore, if there are at least $T_2$ pulls of arm $a$ in the first two levels, 
\[
|\bar{\mu}_a-\mu_a| \leq \sqrt{\frac{2\log(T)}{T_2}}. 
\]
\end{lemma}

\begin{proof}
The events $W_1$ and $W_3^{a,t}$ for $t \geq  (q_a T_1- \GdT \sqrt{T_1\log(T)})S$ together imply that
  \[
    |\bar{\mu}_a - \mu_a| \leq \sqrt{\frac{2\log(T)}{S\left(q_a T_1- \GdT \sqrt{T_1\log(T)}\right)}} \leq \sqrt{\frac{4\log(T)}{S q_a T_1}} .
\]
The last inequality holds when $T$ is larger than some constant.
\end{proof}

\begin{lemma}\label{lem:luck}
  For the $s$-th first-level group and arm $a$, define
  $\bar{\mu}_a^{1,s}$ to be the empirical mean of arm $a$ pulls in
  this group. For each $a \in \{1,2\}$, there exists a group $s_a$
  such that
\[
\bar{\mu}_a ^{1,s_a} > \mu_a + \frac{1}{4\sqrt{q_aT_1}} \quad \mbox{and, } \quad
\bar{\mu}_{3-a} ^{1,s_a} < \mu_{3-a}   - \frac{1}{4\sqrt{q_{3-a} T_1}}.
\]
\end{lemma}

\begin{proof}% [Proof of Lemma~\ref{lem:luck}]
  For each $a \in \{1,2\}$, $W_4$ implies that there exists $s_a$ such
  that both $W_4^{s_a,a,high}$ and $W_4^{s_a,3-a,low}$ happen.  The
  events $W_4^{s_a,a,high}$, $W_1$, $W_2^{s_a,a,t, q_aT_1}$
  for $t = q_a T_1- \GdT \sqrt{T_1\log(T)}+1, ...,q_aT_1-1$ and
  $W_2^{s_a,a,q_aT_1,t}$ for
  $t= q_aT_1,...,q_a T_1+ \GdT \sqrt{T_1\log(T)}$ together imply that
\begin{align*}
\bar{\mu}_a ^{1,s_a} &\geq \mu_a + \left(q_aT_1 \cdot \frac{1}{\sqrt{q_aT_1}} - \GdT \sqrt{T_1\log(T)} \cdot \sqrt{\frac{2\log(T)}{ \GdT \sqrt{T_1\log(T)}}} \right) \cdot \frac{1}{q_a T_1+ \GdT \sqrt{T_1\log(T)}} \\
&> \mu_a + \frac{1}{4\sqrt{q_aT_1}}.
\end{align*}
The second to the last inequality holds when $T$ is larger than some constant.
Similarly, we also have
\[
\bar{\mu}_{3-a} ^{1,s_a} < \mu_{3-a}   - \frac{1}{4\sqrt{q_{3-a} T_1}}.
\]
This completes the proof.
\end{proof}

@@

\begin{proof}[Proof of Lemma~\ref{3levelbigcase} (Large gap case)]
  Observe that for any group $s$ in the first level, the empirical
  means satisfy
\[
\bar{\mu}_1^{1,s} - \bar{\mu}_2^{1,s} \geq \mu_1 -\mu_2 - \sqrt{\frac{4\log(T)}{q_1T_1}} - \sqrt{\frac{4\log(T)}{q_2T_1}} \geq  \sqrt{\frac{4\log(T)}{q_1T_1}} + \sqrt{\frac{4\log(T)}{q_2T_1}}.
\]

For any agent $t$ in the $s$-th second-level group, by Assumption \ref{ass:embehave}, we have
\begin{align*}
\hat{\mu}_1^t - \hat{\mu}_2^t &>\bar{\mu}_1^{1,s} - \bar{\mu}_2^{1,s} - \frac{c_m}{\sqrt{q_1T_1/2}} - \frac{c_m}{\sqrt{q_2T_1/2}}\\
&\geq  \sqrt{\frac{4\log(T)}{q_1T_1}} + \sqrt{\frac{4\log(T)}{q_2T_1}}- \frac{c_m}{\sqrt{q_1T_1/2}} - \frac{c_m}{\sqrt{q_2T_1/2}} > 0
\end{align*}
Therefore, we know agents in the $s$-th second-level group will all pull arm 1.

Now consider the agents in the third level group. Recall $\bar{\mu}_a$
is the empirical mean of arm $a$ in the history they see. We have
\[
\bar{\mu}_1 - \bar{\mu}_2 \geq \mu_1 -\mu_2 - \sqrt{\frac{4\log(T)}{Sq_1T_1}} - \sqrt{\frac{4\log(T)}{Sq_2T_1}} \geq  \sqrt{\frac{4\log(T)}{q_1T_1}} 
+ \sqrt{\frac{4\log(T)}{q_2T_1}}.
\]
Similarly as above, by Assumption \ref{ass:embehave}, we know
$\hat{\mu}_1^t - \hat{\mu}_2^t > 0$ for any agent $t$ in the third
level. Therefore, the agents in the third-level group will all pull
arm 1.  \OMIT{Therefore the expected regret is at most
  $S \GdT T_1 = O(T^{4/7} \log^{6/7}(T))$.}
\end{proof}

\begin{proof}[Proof of Lemma~\ref{3levelmedium} (Medium gap case)]
  % $2\left(\sqrt{\frac{4\log(T)}{Sq_1T_1}} +
  %   \sqrt{\frac{4\log(T)}{Sq_2T_1}}\right) \leq \mu_1-\mu_2 <
  % 2\left(\sqrt{\frac{4\log(T)}{q_1T_1}} +
  %   \sqrt{\frac{4\log(T)}{q_2T_1}}\right)$. 
  Recall $\bar{\mu}_a$ is
  the empirical mean of arm $a$ in the first two levels. We have
\[
\bar{\mu}_1 - \bar{\mu}_2 \geq \mu_1 -\mu_2 - \sqrt{\frac{4\log(T)}{Sq_1T_1}} - \sqrt{\frac{4\log(T)}{Sq_2T_1}} \geq  \sqrt{\frac{4\log(T)}{Sq_1T_1}} 
+ \sqrt{\frac{4\log(T)}{Sq_2T_1}}.
\]
For any agent $t$ in the third level, by Assumption \ref{ass:embehave}, we have
\begin{align*}
\hat{\mu}_1^t - \hat{\mu}_2^t &>\bar{\mu}_1 - \bar{\mu}_2 - \frac{c_m}{\sqrt{Sq_1T_1/2}} - \frac{c_m}{\sqrt{Sq_2T_1/2}}\\
&\geq  \sqrt{\frac{4\log(T)}{Sq_1T_1}} + \sqrt{\frac{4\log(T)}{Sq_2T_1}}- \frac{c_m}{\sqrt{Sq_1T_1/2}} - \frac{c_m}{\sqrt{Sq_2T_1/2}}\\
 &> 0.
\end{align*}
So we know agents in the third-level group will all pull arm 1. \OMIT{Therefore the expected regret is at most 
\[
(S \GdT T_1 + S T_2) \cdot 2\left(\sqrt{\frac{4\log(T)}{q_1T_1}} 
+ \sqrt{\frac{4\log(T)}{q_2T_1}}\right) = O(T^{4/7} \log^{6/7}(T))
\]
}
\end{proof}

\begin{proof}[Proof of Lemma~\ref{3levelsmallcase} (Small gap case)]
  % $ 3\sqrt{\frac{2\log(T)}{T_2}} < \mu_1-\mu_2 <
  % 2\left(\sqrt{\frac{4\log(T)}{Sq_1T_1}} +
  %   \sqrt{\frac{4\log(T)}{Sq_2T_1}}\right)$.  
  In this case, we need both arms to be pulled at least $T_2$ rounds
  in the second level. For every arm $a$, consider the $s_a$-th
  second-level group, with $s_a$ given by Lemma~\ref{lem:luck}. We
  have
\begin{align*}
\bar{\mu}_a^{1,s_a} - \bar{\mu}_{3-a}^{1,s_a} &> \mu_a + \frac{1}{4\sqrt{q_aT_1}} -\mu_{3-a} +\frac{1}{4\sqrt{q_{3-a}T_1}} \\
&> \frac{1}{4\sqrt{q_1T_1}}+ \frac{1}{4\sqrt{q_2T_1}} - 2\left(\sqrt{\frac{4\log(T)}{Sq_1T_1}} 
+ \sqrt{\frac{4\log(T)}{Sq_2T_1}}\right) \\
&\geq \frac{1}{8\sqrt{q_1T_1}}+ \frac{1}{8\sqrt{q_2T_1}}.
\end{align*}
For any agent $t$ in the $s_a$-th second-level group, by Assumption \ref{ass:embehave}, we have
\begin{align*}
\hat{\mu}_a^t - \hat{\mu}_{3-a}^t &>\bar{\mu}_a^{1,s_a} - \bar{\mu}_{3-a}^{1,s_a} - \frac{c_m}{\sqrt{q_1T_1/2}} - \frac{c_m}{\sqrt{q_2T_1/2}}\\
&\geq   \frac{1}{8\sqrt{q_1T_1}}+ \frac{1}{8\sqrt{q_2T_1}}- \frac{c_m}{\sqrt{q_1T_1/2}} - \frac{c_m}{\sqrt{q_2T_1/2}}\\
 &> 0.
\end{align*}
So we know agents in the $s_a$-th second-level group will all pull arm $a$. Therefore in the first two levels, both arms are pulled at least $T_2$ times. Now consider the third-level. We have
\[
\bar{\mu}_1 - \bar{\mu}_2  \geq \mu_1 -\mu_2 - 2\sqrt{\frac{2\log(T)}{T_2}} \geq \sqrt{\frac{2\log(T)}{T_2}}.
\]
Similarly as above, by Assumption \ref{ass:embehave}, we know $\hat{\mu}_1^t - \hat{\mu}_2^t > 0$ for any agent $t$ in the third level. So we know agents in the third-level group will all pull arm 1.\OMIT{
Therefore the expected regret is at most 
\[
(S \GdT T_1 + S T_2) \cdot 2\left(\sqrt{\frac{4\log(T)}{Sq_1T_1}} 
+ \sqrt{\frac{4\log(T)}{Sq_2T_1}}\right) \leq O(T^{4/7} \log^{6/7}(T))
\]
}
\end{proof}

>>>>

\begin{proof}[Proof of Lemma~\ref{3levelw1}]
  For the $s$-th first-level group, define $W_1^{a,s}$ to be the event
  that the number of arm $a$ pulls in the $s$-th first-level group is
  between $\fdpN T_1- \GdT \sqrt{T_1\log(T)}$ and
  $\fdpN T_1 + \GdT \sqrt{T_1\log(T)}$. By Lemma~\ref{lem:t1runs}
\[
\Pr[W_1^{a,s}] \geq 1-2\exp(-2\log(T)) \geq 1-2/T^2.
\]
Let $W_1$  be the intersection of all these events (i.e.
$W_1 = \bigcap_{a,s}W_1^{a,s}$). By union bound, we have
\[
\Pr[W_1] \geq 1- \frac{4S}{T^2}.
\]
\end{proof}

@@

\begin{proof}[Proof of Lemma~\ref{3levelw4}]
By Berry-Esseen Theorem and
  $\mu_a \in [1/3,2/3]$, we have for any $a$,
\[
\Pr[W_4^{s,a,high}] \geq (1-\Phi(1/2)) - \frac{5}{\sqrt{\fdpN T_1}} > 1/4.
\]
The last inequality follows when $T$ is larger than some constant.
Similarly we also have 
\[
\Pr[W_4^{s,a,low}] > 1/4.
\]
Since $W_4^{s,a,high}$ is independent with $W_4^{s,3-a,low}$, we have
\[
\Pr[W_4^{s,a,high} \cap W_4^{s,3-a,low}] =\Pr[W_4^{s,a,high}] \cdot  \Pr[W_4^{s,3-a,low}]>(1/4)^2 = 1/16.
\]
Notice that $(W_4^{s,a,high} \cap W_4^{s,3-a,low})$ are independent
across different $s$'s. By union bound, we have
\[
\Pr[W_4] \geq 1- 2(1-1/16)^S \geq 1 -2 /T.
\]
\end{proof}

@@

\begin{lemma}
  For the $s$-th first-level group and arm $a$, define
  $\bar{\mu}_a^{1,s}$ to be the empirical mean of arm $a$ pulls in
  this group. If $W$ holds, then
  \[
    |\bar{\mu}_a^{1,s} - \mu_a| \leq \sqrt{\frac{4\log(T)}{\fdpN T_1}}.
  \]
\end{lemma}

\begin{proof}
  The events $W_1$ and $W_2^{a,s,1,t}$ for
  $t = \fdpN T_1- \GdT \sqrt{T_1\log(T)},...,\fdpN T_1 + \GdT
  \sqrt{T_1\log(T)}$ together imply that
\[
|\bar{\mu}_a^{1,s} - \mu_a| \leq \sqrt{\frac{2\log(T)}{\fdpN T_1- \GdT \sqrt{T_1\log(T)}}} \leq \sqrt{\frac{4\log(T)}{\fdpN T_1}}.
\]
The last inequality holds when $T$ is larger than some constant.
\end{proof}

\begin{lemma}
  For each arm $a$, define $\bar{\mu}_a$ to be the empirical mean of
  arm $a$ pulls in the first two levels. If $W$ holds, then
  \[
    |\bar{\mu}_a - \mu_a| \leq \sqrt{\frac{4\log(T)}{S \fdpN T_1}} .
  \]
Furthermore, if there are at least $T_2$ pulls of arm $a$ in the first two levels, 
\[
|\bar{\mu}_a-\mu_a| \leq \sqrt{\frac{2\log(T)}{T_2}}. 
\]
\end{lemma}

\begin{proof}
The events $W_1$ and $W_3^{a,t}$ for $t \geq  (\fdpN T_1- \GdT \sqrt{T_1\log(T)})S$ together imply that
  \[
    |\bar{\mu}_a - \mu_a| \leq \sqrt{\frac{2\log(T)}{S\left(\fdpN T_1- \GdT \sqrt{T_1\log(T)}\right)}} \leq \sqrt{\frac{4\log(T)}{S \fdpN T_1}} .
\]
The last inequality holds when $T$ is larger than some constant.
\end{proof}

\begin{lemma}\label{lem:luck}
  For the $s$-th first-level group and arm $a$, define
  $\bar{\mu}_a^{1,s}$ to be the empirical mean of arm $a$ pulls in
  this group. For each $a \in \{1,2\}$, there exists a group $s_a$
  such that
\[
\bar{\mu}_a ^{1,s_a} > \mu_a + \frac{1}{4\sqrt{\fdpN T_1}} \quad \mbox{and, } \quad
\bar{\mu}_{3-a} ^{1,s_a} < \mu_{3-a}   - \frac{1}{4\sqrt{\fdpN[3-a] T_1}}.
\]
\end{lemma}

\begin{proof}% [Proof of Lemma~\ref{lem:luck}]
  For each $a \in \{1,2\}$, $W_4$ implies that there exists $s_a$ such
  that both $W_4^{s_a,a,high}$ and $W_4^{s_a,3-a,low}$ happen.  The
  events $W_4^{s_a,a,high}$, $W_1$, $W_2^{s_a,a,t, \fdpN T_1}$
  for $t = \fdpN T_1- \GdT \sqrt{T_1\log(T)}+1, ...,\fdpN T_1-1$ and
  $W_2^{s_a,a,\fdpN T_1,t}$ for
  $t= \fdpN T_1,...,\fdpN T_1+ \GdT \sqrt{T_1\log(T)}$ together imply that
\begin{align*}
\bar{\mu}_a ^{1,s_a} &\geq \mu_a + \left(\fdpN T_1 \cdot \frac{1}{\sqrt{\fdpN T_1}} - \GdT \sqrt{T_1\log(T)} \cdot \sqrt{\frac{2\log(T)}{ \GdT \sqrt{T_1\log(T)}}} \right) \cdot \frac{1}{\fdpN T_1+ \GdT \sqrt{T_1\log(T)}} \\
&> \mu_a + \frac{1}{4\sqrt{\fdpN T_1}}.
\end{align*}
The second to the last inequality holds when $T$ is larger than some constant.
Similarly, we also have
\[
\bar{\mu}_{3-a} ^{1,s_a} < \mu_{3-a}   - \frac{1}{4\sqrt{\fdpN[3-a] T_1}}.
\]
This completes the proof.
\end{proof}

@@

\begin{proof}[Proof of Lemma~\ref{3levelbigcase} (Large gap case)]
  Observe that for any group $s$ in the first level, the empirical
  means satisfy
\[
\bar{\mu}_1^{1,s} - \bar{\mu}_2^{1,s} \geq \mu_1 -\mu_2 - \sqrt{\frac{4\log(T)}{\fdpN[1]T_1}} - \sqrt{\frac{4\log(T)}{\fdpN[2]T_1}} \geq  \sqrt{\frac{4\log(T)}{\fdpN[1]T_1}} + \sqrt{\frac{4\log(T)}{\fdpN[2]T_1}}.
\]

For any agent $t$ in the $s$-th second-level group, by Assumption \ref{ass:embehave}, we have
\begin{align*}
\hat{\mu}_1^t - \hat{\mu}_2^t &>\bar{\mu}_1^{1,s} - \bar{\mu}_2^{1,s} - \frac{c_m}{\sqrt{\fdpN[1]T_1/2}} - \frac{c_m}{\sqrt{\fdpN[2]T_1/2}}\\
&\geq  \sqrt{\frac{4\log(T)}{\fdpN[1]T_1}} + \sqrt{\frac{4\log(T)}{\fdpN[2]T_1}}- \frac{c_m}{\sqrt{\fdpN[1]T_1/2}} - \frac{c_m}{\sqrt{\fdpN[2]T_1/2}} > 0
\end{align*}
Therefore, we know agents in the $s$-th second-level group will all pull arm 1.

Now consider the agents in the third level group. Recall $\bar{\mu}_a$
is the empirical mean of arm $a$ in the history they see. We have
\[
\bar{\mu}_1 - \bar{\mu}_2 \geq \mu_1 -\mu_2 - \sqrt{\frac{4\log(T)}{S\fdpN[1]T_1}} - \sqrt{\frac{4\log(T)}{S\fdpN[2]T_1}} \geq  \sqrt{\frac{4\log(T)}{\fdpN[1]T_1}} 
+ \sqrt{\frac{4\log(T)}{\fdpN[2]T_1}}.
\]
Similarly as above, by Assumption \ref{ass:embehave}, we know
$\hat{\mu}_1^t - \hat{\mu}_2^t > 0$ for any agent $t$ in the third
level. Therefore, the agents in the third-level group will all pull
arm 1.  \OMIT{Therefore the expected regret is at most
  $S \GdT T_1 = O(T^{4/7} \log^{6/7}(T))$.}
\end{proof}

\begin{proof}[Proof of Lemma~\ref{3levelmedium} (Medium gap case)]
  % $2\left(\sqrt{\frac{4\log(T)}{S\fdpN[1]T_1}} +
  %   \sqrt{\frac{4\log(T)}{S\fdpN[2]T_1}}\right) \leq \mu_1-\mu_2 <
  % 2\left(\sqrt{\frac{4\log(T)}{\fdpN[1]T_1}} +
  %   \sqrt{\frac{4\log(T)}{\fdpN[2]T_1}}\right)$. 
  Recall $\bar{\mu}_a$ is
  the empirical mean of arm $a$ in the first two levels. We have
\[
\bar{\mu}_1 - \bar{\mu}_2 \geq \mu_1 -\mu_2 - \sqrt{\frac{4\log(T)}{S\fdpN[1]T_1}} - \sqrt{\frac{4\log(T)}{S\fdpN[2]T_1}} \geq  \sqrt{\frac{4\log(T)}{S\fdpN[1]T_1}} 
+ \sqrt{\frac{4\log(T)}{S\fdpN[2]T_1}}.
\]
For any agent $t$ in the third level, by Assumption \ref{ass:embehave}, we have
\begin{align*}
\hat{\mu}_1^t - \hat{\mu}_2^t &>\bar{\mu}_1 - \bar{\mu}_2 - \frac{c_m}{\sqrt{S\fdpN[1]T_1/2}} - \frac{c_m}{\sqrt{S\fdpN[2]T_1/2}}\\
&\geq  \sqrt{\frac{4\log(T)}{S\fdpN[1]T_1}} + \sqrt{\frac{4\log(T)}{S\fdpN[2]T_1}}- \frac{c_m}{\sqrt{S\fdpN[1]T_1/2}} - \frac{c_m}{\sqrt{S\fdpN[2]T_1/2}}\\
 &> 0.
\end{align*}
So we know agents in the third-level group will all pull arm 1. \OMIT{Therefore the expected regret is at most 
\[
(S \GdT T_1 + S T_2) \cdot 2\left(\sqrt{\frac{4\log(T)}{\fdpN[1]T_1}} 
+ \sqrt{\frac{4\log(T)}{\fdpN[2]T_1}}\right) = O(T^{4/7} \log^{6/7}(T))
\]
}
\end{proof}

\begin{proof}[Proof of Lemma~\ref{3levelsmallcase} (Small gap case)]
  % $ 3\sqrt{\frac{2\log(T)}{T_2}} < \mu_1-\mu_2 <
  % 2\left(\sqrt{\frac{4\log(T)}{S\fdpN[1]T_1}} +
  %   \sqrt{\frac{4\log(T)}{S\fdpN[2]T_1}}\right)$.  
  In this case, we need both arms to be pulled at least $T_2$ rounds
  in the second level. For every arm $a$, consider the $s_a$-th
  second-level group, with $s_a$ given by Lemma~\ref{lem:luck}. We
  have
\begin{align*}
\bar{\mu}_a^{1,s_a} - \bar{\mu}_{3-a}^{1,s_a} &> \mu_a + \frac{1}{4\sqrt{\fdpN T_1}} -\mu_{3-a} +\frac{1}{4\sqrt{\fdpN[3-a]T_1}} \\
&> \frac{1}{4\sqrt{\fdpN[1]T_1}}+ \frac{1}{4\sqrt{\fdpN[2]T_1}} - 2\left(\sqrt{\frac{4\log(T)}{S\fdpN[1]T_1}} 
+ \sqrt{\frac{4\log(T)}{S\fdpN[2]T_1}}\right) \\
&\geq \frac{1}{8\sqrt{\fdpN[1]T_1}}+ \frac{1}{8\sqrt{\fdpN[2]T_1}}.
\end{align*}
For any agent $t$ in the $s_a$-th second-level group, by Assumption \ref{ass:embehave}, we have
\begin{align*}
\hat{\mu}_a^t - \hat{\mu}_{3-a}^t &>\bar{\mu}_a^{1,s_a} - \bar{\mu}_{3-a}^{1,s_a} - \frac{c_m}{\sqrt{\fdpN[1]T_1/2}} - \frac{c_m}{\sqrt{\fdpN[2]T_1/2}}\\
&\geq   \frac{1}{8\sqrt{\fdpN[1]T_1}}+ \frac{1}{8\sqrt{\fdpN[2]T_1}}- \frac{c_m}{\sqrt{\fdpN[1]T_1/2}} - \frac{c_m}{\sqrt{\fdpN[2]T_1/2}}\\
 &> 0.
\end{align*}
So we know agents in the $s_a$-th second-level group will all pull arm $a$. Therefore in the first two levels, both arms are pulled at least $T_2$ times. Now consider the third-level. We have
\[
\bar{\mu}_1 - \bar{\mu}_2  \geq \mu_1 -\mu_2 - 2\sqrt{\frac{2\log(T)}{T_2}} \geq \sqrt{\frac{2\log(T)}{T_2}}.
\]
Similarly as above, by Assumption \ref{ass:embehave}, we know $\hat{\mu}_1^t - \hat{\mu}_2^t > 0$ for any agent $t$ in the third level. So we know agents in the third-level group will all pull arm 1.\OMIT{
Therefore the expected regret is at most 
\[
(S \GdT T_1 + S T_2) \cdot 2\left(\sqrt{\frac{4\log(T)}{S\fdpN[1]T_1}} 
+ \sqrt{\frac{4\log(T)}{S\fdpN[2]T_1}}\right) \leq O(T^{4/7} \log^{6/7}(T))
\]
}
\end{proof}

### 2018-11-01 app-warmup.tex
q_a -> \fdpN
fun fact: we now have at most 30 q's in the paper

% \begin{itemize}
  \OMIT{\paragraph{Concentration of the number of arm $a$ pulls in the first
    level.}
By Lemma \ref{lem:greedy}, we know $\GdP \leq q_a \leq \GdT$.}
  Define $W_1^a$ to be the event that the number of arm $a$ pulls in
  the first level is at least $q_a T_1- \GdT \sqrt{T_1\log(T)}$.
  \swedit{As long as we set $T_1 \geq \frac{4(\GdT)^2}{(\GdP)^2}\log(T)$,
    this implies that the number of arm $a$ pulls is then at least
    $q_a T_1/2$.}
\OMIT{  By Chernoff bound,
  \[
    \Pr[W_1^a] \geq 1-\exp(-2\log(T)) \geq 1-1/T^2.
  \]
}
Define $W_1$ to be the intersection of all these events (i.e. $W_1 = \bigcap_{a}W_1^a$). By Lemma~\ref{lem:t1runs}, we have
\[
\Pr[W_1] \geq 1- \frac{K}{T^2} \geq 1 - \frac{1}{T}.
\]
\OMIT{\paragraph{Concentration of the empirical mean of arm $a$ pulls
    in the first level.}}  Next, we show that the empirical mean of
each arm $a$ is close to the true mean. To facilitate our reasoning,
let us imagine there is a tape of length $T$ for each arm $a$, with
each cell containing an independent draw of the realized reward from
the distribution $\cD_a$. Then for each arm $a$ and any $N\in [T]$, we
can think of the sequence of the first $N$ realized rewards of $a$
coming from the prefix of $N$ cells in its reward tape. Define
$W^{a,t}_2$ to be the event that the empirical mean of the first $t$
\swedit{realized rewards in the tape} of arm $a$ is at most
$\sqrt{\frac{2\log(T)}{t}}$ away from $\mu_a$. Define $W_2$ to be the
intersection of these events (i.e.  $\bigcap_{a,t} W^{a,t}_2$).  By
Chernoff bound,\swcomment{$t$ may be confusing here}
\[
\Pr[W^{a,t}_2] \geq 1 - 2\exp(-4\log(T)) \geq 1-2/T^4.
\]
By union bound,
\[
\Pr[W_2] \geq 1 - KT \cdot \frac{2}{T^4} \geq 1 - \frac{2}{T}.
\]

@@

For any arm $a$ and agent $t$ in the second level, by $W_1$ and $W_2$, we have
\[
|\bar{\mu}^t_a - \mu_a| \leq \sqrt{\frac{2\log(T)}{q_aT_1 /2}}.
\]
By $W_1$ and Assumption \ref{ass:embehave}, we have
\[
|\bar{\mu}^t_a - \hat{\mu}^t_a| \leq \frac{c_m}{\sqrt{q_aT_1/2}}.
\]
Therefore,
\[
|\hat{\mu}^t_a - \mu_a|\leq \sqrt{\frac{2\log(T)}{q_aT_1 /2}}+\frac{c_m}{\sqrt{q_aT_1/2}} \leq 3 \sqrt{\frac{\log(T)}{\GdP T_1 }}.
\]
So the second-level agents will pick an arm $a$ which has $\mu_a$ at most $6 \sqrt{\frac{\log(T)}{\GdP T_1 }}$ away from $\mu_1$. To sum up, the total expected regret is at most
\[
T_1 \cdot \GdT + T \cdot (1-\Pr[W_1 \cap W_2]) + T \cdot  6 \sqrt{\frac{\log(T)}{\GdP T_1 }}.
\]
By setting $T_1 = T^{2/3}\log(T)^{1/3}$, we get expected regret $O(T^{2/3}\log(T)^{1/3})$.
\OMIT{Notice that if we know the gap parameter is known to be larger than
$\Delta$, we can set
\[
T_1 = \max\left( \frac{4\GdT^2}{\GdP^2}\log(T), \frac{36 }{\Delta^2 \cdot p_G} \log(T) \right).
\]
In this case, since $\Delta \geq 6 \sqrt{\frac{\log(T)}{\GdP T_1 }}$, we know agents in the second level will all pull arm 1. Therefore, the total expected regret is at most
\[
T_1 \cdot \GdT + T \cdot (1- \Pr[W_1 \cap W_2]) = O(\Delta^{-2} \log(T)).
\]
This completes the proof.}
\end{proof}

>>>>

% \begin{itemize}
  \OMIT{\paragraph{Concentration of the number of arm $a$ pulls in the first
    level.}
By Lemma \ref{lem:greedy}, we know $\GdP \leq \fdpN \leq \GdT$.}
  Define $W_1^a$ to be the event that the number of arm $a$ pulls in
  the first level is at least $\fdpN T_1- \GdT \sqrt{T_1\log(T)}$.
  \swedit{As long as we set $T_1 \geq \frac{4(\GdT)^2}{(\GdP)^2}\log(T)$,
    this implies that the number of arm $a$ pulls is then at least
    $\fdpN T_1/2$.}
\OMIT{  By Chernoff bound,
  \[
    \Pr[W_1^a] \geq 1-\exp(-2\log(T)) \geq 1-1/T^2.
  \]
}
Define $W_1$ to be the intersection of all these events (i.e. $W_1 = \bigcap_{a}W_1^a$). By Lemma~\ref{lem:t1runs}, we have
\[
\Pr[W_1] \geq 1- \frac{K}{T^2} \geq 1 - \frac{1}{T}.
\]
\OMIT{\paragraph{Concentration of the empirical mean of arm $a$ pulls
    in the first level.}}  Next, we show that the empirical mean of
each arm $a$ is close to the true mean. To facilitate our reasoning,
let us imagine there is a tape of length $T$ for each arm $a$, with
each cell containing an independent draw of the realized reward from
the distribution $\cD_a$. Then for each arm $a$ and any $N\in [T]$, we
can think of the sequence of the first $N$ realized rewards of $a$
coming from the prefix of $N$ cells in its reward tape. Define
$W^{a,t}_2$ to be the event that the empirical mean of the first $t$
\swedit{realized rewards in the tape} of arm $a$ is at most
$\sqrt{\frac{2\log(T)}{t}}$ away from $\mu_a$. Define $W_2$ to be the
intersection of these events (i.e.  $\bigcap_{a,t} W^{a,t}_2$).  By
Chernoff bound,\swcomment{$t$ may be confusing here}
\[
\Pr[W^{a,t}_2] \geq 1 - 2\exp(-4\log(T)) \geq 1-2/T^4.
\]
By union bound,
\[
\Pr[W_2] \geq 1 - KT \cdot \frac{2}{T^4} \geq 1 - \frac{2}{T}.
\]

@@

For any arm $a$ and agent $t$ in the second level, by $W_1$ and $W_2$, we have
\[
|\bar{\mu}^t_a - \mu_a| \leq \sqrt{\frac{2\log(T)}{\fdpN T_1 /2}}.
\]
By $W_1$ and Assumption \ref{ass:embehave}, we have
\[
|\bar{\mu}^t_a - \hat{\mu}^t_a| \leq \frac{c_m}{\sqrt{\fdpN T_1/2}}.
\]
Therefore,
\[
|\hat{\mu}^t_a - \mu_a|\leq \sqrt{\frac{2\log(T)}{\fdpN T_1 /2}}+\frac{c_m}{\sqrt{\fdpN T_1/2}} \leq 3 \sqrt{\frac{\log(T)}{\GdP T_1 }}.
\]
So the second-level agents will pick an arm $a$ which has $\mu_a$ at most $6 \sqrt{\frac{\log(T)}{\GdP T_1 }}$ away from $\mu_1$. To sum up, the total expected regret is at most
\[
T_1 \cdot \GdT + T \cdot (1-\Pr[W_1 \cap W_2]) + T \cdot  6 \sqrt{\frac{\log(T)}{\GdP T_1 }}.
\]
By setting $T_1 = T^{2/3}\log(T)^{1/3}$, we get expected regret $O(T^{2/3}\log(T)^{1/3})$.
\OMIT{Notice that if we know the gap parameter is known to be larger than
$\Delta$, we can set
\[
T_1 = \max\left( \frac{4\GdT^2}{\GdP^2}\log(T), \frac{36 }{\Delta^2 \cdot p_G} \log(T) \right).
\]
In this case, since $\Delta \geq 6 \sqrt{\frac{\log(T)}{\GdP T_1 }}$, we know agents in the second level will all pull arm 1. Therefore, the total expected regret is at most
\[
T_1 \cdot \GdT + T \cdot (1- \Pr[W_1 \cap W_2]) = O(\Delta^{-2} \log(T)).
\]
This completes the proof.}
\end{proof}
